---
title: "Tidy Models"
author: "Arvind Venkatadri"
date: "3/9/2020"
output:
  github_document: default
  pdf_document:
    toc: yes
    latex_engine: xelatex
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
  html_document:
    df_print: default #kable/tibble/paged
    toc: yes
    toc_depth: 4
    toc_float: true
    theme : darkly
    number_sections: true
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages(c("tidyverse", "tidymodels", "remotes","rpart.plot", "rattle", "vip", "AmesHousing", "kknn", "rpart", "ranger", "partykit"))

# remotes::install_github(c("tidymodels/workflows","tidymodels/tune", "tidymodels/modeldata"))
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)

# AmesHousing: Descriptions of 2,930 houses sold in Ames, IA ( Where Jane Smiley lives) from 2006 to 2010, collected by the Ames Assessor’s Office.

ames <- AmesHousing::make_ames() %>% 
  dplyr::select(-matches("Qu"))
glimpse(ames)

# Fit a linear model
lm_ames <- lm(data = ames, Sale_Price ~ Gr_Liv_Area)
lm_ames
# ?formula for help
summary(lm_ames)

```
Hypothesis -> Explains -> Reality
Model -> Matches? -> Data
Hypothesis -> Model based on how well model matches data.
TBD: put this into UML.

The `parsnip` package is a successor to `caret'.
To model with `parsnip`:
1. Pick a `model` : check [here](https://tidymodels.github.io/parsnip/articles/articles/Models.html) for models available in `tidymodels`
2. Set the `engine`
3. Set the `mode` ( if needed)

```{r parsnip-1}
decision_tree() %>% 
  set_engine("C5.0") %>% 
  set_mode("classification")

nearest_neighbor() %>% 
  set_engine("kknn") %>% 
  set_mode("regression")

linear_reg(mode = "regression", # default mode
  penalty = NULL, # Model hyperparameter
  mixture = NULL) # Model hyperparameter

lm_spec <- linear_reg() %>% 
  set_engine(engine = "lm")
lm_spec # a parsnip model

lm_fit <- fit_data(Sale_Price ~ Gr_Liv_Area, model = lm_spec, data = ames)
# Check if lm_fit and lm_ames give the same results. 

lm_fit
lm_ames
```

```{r}
lm_fit %>% predict(new_data = ames)
```

Use predict() to

 - Use your linear model to predict sale prices; save the tibble as `price_pred`
- Add a pipe and use mutate() to add a column with the observed sale prices; name it `truth`
- Hint: Be sure to remove every _ before running the code!

```{r}
price_pred <- predict(lm_fit, new_data = ames) %>% 
  dplyr::mutate(price_truth = ames$Sale_Price)
price_pred

yardstick::rmse(price_pred,truth = price_truth ,estimate = .pred)
```
We test the model using data splits into training data and (holdout) test data
```{r Testing}
set.seed(100)
ames_split <- initial_split(ames, prop = 3/4)
ames_split
train_set <- training(ames_split)
test_set <- testing(ames_split)
train_set
test_set

my_mod <- linear_reg() %>% 
  set_engine(engine = "lm")

my_fit <- fit_data(Sale_Price ~ Gr_Liv_Area,
                   model = my_mod,
                   data = train_set)

price_pred <- predict(my_fit, new_data = test_set) %>% 
  dplyr::mutate(price_truth = test_set$Sale_Price)
price_pred
testing_rmse <- yardstick::rmse(price_pred,truth = price_truth, ,estimate = .pred)
testing_rmse

# How to find "training RMSE"? NOT WORKING...NOT UNDERSTOOD
train_pred <- predict(my_fit, new_data = train_set) %>% 
  dplyr::mutate(true_price = train_set$Sale_Price)
training_rmse <- yardstick::rmse(train_pred,truth = true_price,estimate = .pred)
testing_rmse
```

We can do ** Stratified Sampling** instead of random sampling.

```{r stratified sampling}

```

